Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/empirical-comparison.tex
shortening to 8 pages

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/strong3}
\caption{The cumulative number of mistakes versus the number of rounds,
in the strongly separable case (\autoref{figure:strongly-separable-dataset}) for various algorithms.}
\label{figure:number-of-mistakes-strongly-separable-dataset}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/weak3}
\caption{The cumulative number of mistakes versus the number of rounds,
in the weakly separable case (\autoref{figure:weakly-separable-dataset}) for various algorithms.}
\label{figure:number-of-mistakes-weakly-separable-dataset}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.42\textwidth]{figures/strong3}
\caption{The cumulative number of mistakes versus the number of rounds,
in the strongly separable distribution of \autoref{figure:strongly-separable-dataset} for various algorithms.}
\label{figure:number-of-mistakes-strongly-separable-dataset}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.42\textwidth]{figures/weak3}
\caption{The cumulative number of mistakes versus the number of rounds,
in the weakly separable distribution of \autoref{figure:weakly-separable-dataset} for various algorithms.}
\label{figure:number-of-mistakes-weakly-separable-dataset}
\end{figure}

### 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
shortening to 8 pages

The rational kernel $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
\begin{equation}
\label{equation:rational-kernel}
k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
\end{equation}
Note that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.

@@

We give two explicit constructions for such polynomial in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}.
Our constructions are based on \citet{Klivans-Servedio-2008} which in turn uses
the constructions from~\citet{Beigel-Reingold-Spielman-1995}. More importantly,
the theorems quantify certain parameters of the polynomial, which will allow us
to give an upper bound on the transformed margin $\gamma'$.

@@

The proofs of the theorems can be found in
Appendix~\ref{section:proof-of-polynomial-approximation} in the supplementary
material. The geometric interpretation of the two regions described in parts 1
and 2 of the theorems is explained in Figure~\ref{figure:pizza-slice}. Similar
but weaker results were proved by~\citet{Klivans-Servedio-2008}. In particular,
our bounds in parts 1, 2, 3, 4 of
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
are independent of the dimension $d$.

>>>>

The rational kernel $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
\begin{equation}
\label{equation:rational-kernel}
k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
\end{equation}
Note that $k(x,x')$ can be evaluated in $O(d)$ time.

@@

We give two explicit constructions for such polynomial in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}.
Our constructions are based on \citet{Klivans-Servedio-2008} which in turn uses
the constructions from~\citet{Beigel-Reingold-Spielman-1995}. More importantly,
the theorems quantify certain parameters of the polynomial, which allows us
to upper bound the transformed margin $\gamma'$.

@@

The proofs of the theorems are in
Appendix~\ref{section:proof-of-polynomial-approximation}.
The geometric interpretation of the two regions described in parts 1
and 2 of the theorems is explained in Figure~\ref{figure:pizza-slice}. Similar
but weaker results were proved by~\citet{Klivans-Servedio-2008}. Specifically,
our bounds in parts 1, 2, 3, 4 of
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
are independent of the dimension $d$.

### 2019-01-23 ICML-submission/notions-of-linear-separability.tex
shortening to 8 pages

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable
with a positive margin $\gamma$ but is not strongly linearly separable with
any positive margin $\gamma$. An example of such set of labeled examples is
shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.

>>>>

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable
with a positive margin $\gamma$ but is not strongly linearly separable with
any positive margin.~\autoref{figure:weakly-linearly-separable-examples-with-margin}
shows one such set of labeled examples.
